---
output:
  word_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

# Module 2 - Assignment2

## Pusarla, Praveen

## Introduction to R Markdown

This is the first *R Markdown document* for the MBA-503 Programming for Analytics.
In this assignment we will go over the previous topics covered in Module1 classes including atomic vectors, data frames and data types.

Now we will be reviewing the **question2** of module1 assignments related to Loading Packages and Plotting data. We will be plotting a basic graph showing sales over the past 6 months.



```{r Plot of Sales by Month}
library("tidyverse")
sales<-c(50,150,200,100,300,250)
month<-(1:6)
qplot(month,sales)
```


The month with largest sales is Obtained by running which.max(q2_sales$sales) and it is Month **5**.
The sales amount for that month can be obtained by running max(sales) and it is **300**.




Now let us review **question4** of module1 assignment related to working with Data Frames.  



```{r Working with Data Frames}
months<-c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct","Nov", "Dec")
Sales <-c(150.25, 258.54, 268.55, 122.52, 987, 458.82, 667.23, 845.54, 586.78, 888.58, 756.12, 456.84)
Yearly_sales<-data_frame(months,Sales)
Yearly_sales
#View(Yearly_sales)
which.max(Yearly_sales$Sales)
which.min(Yearly_sales$Sales)
qplot(months,Sales)
```


Month with most sales is **May**. It is obtained by Run the command which.max(Yearly_sales$Sales) to know the row position in the data frame.


Month with least sales is **Apr** which is obtained by Run the command which.min(Yearly_sales$Sales) to know the row position in the data frame.

