---
output:
  word_document: default
  html_document: default
editor_options: 
  chunk_output_type: inline
---
# Module 3 - Assignment 1
## Pusarla, Praveenkumar
### Data Visualization

We are using the datasets containing candy rankings and production that are attached in the the Canvas course website. The CSV files candy_data and candy_production should be loaded to complete this assignment.

```{r Loading packages and data sets}
library(tidyverse)
candy_data <- read_csv("candy_data.csv")
candy_production <- read_csv("candy_production.csv", 
    col_types = cols(observation_date = col_date(format = "%Y-%m-%d")))
head(candy_data)
head(candy_production)
```

#### Visualization with Scatterplots (geom_point)

To build a scatterplot to compare the sugar content to price of various types of candy on the market

```{r Scaterplot}
ggplot(data = candy_data, aes (x=sugarpercent,y=pricepercent)) +
  geom_point()

```


To visual representation of how closely sugarpercent and pricepercent are related to each other, and the strength of that relationship


```{r Scaterpolt to view reationship}
ggplot(data = candy_data, aes (x=sugarpercent,y=pricepercent)) +
  geom_point() +
  geom_smooth(method = "lm")

```

To know what each dot represents an additional argument is needed in the aes() command to include a label.

```{r Scaterplot with labeling each point}
ggplot(data = candy_data, aes (x=sugarpercent,y=pricepercent,  label = competitorname)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  geom_text() 

```

Formatting the name of the dots to appear properly and easy to read.


```{r Scatorplot - Making the labeling more readable}
ggplot(data = candy_data, aes (x=sugarpercent,y=pricepercent,  label = competitorname)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  geom_text(check_overlap = T,
            vjust = "bottom",
            nudge_y = 0.01,
            angle = 30,
            size = 2 
            )

```


Adding title and proper naming of the X and Y axis


```{r Sacaterplot with Proper title and labeling}
ggplot(data = candy_data, aes (x=sugarpercent,y=pricepercent,  label = competitorname)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  geom_text(check_overlap = T,
            vjust = "bottom",
            nudge_y = 0.01,
            angle = 30,
            size = 2 
            ) +
  labs(title = "Sugar by Price Scatterplot",
 x = "Sugar content (percentile)", 
 y = "Price (percentile)"
 )
```

From the graph we can clearly say that **ReeseÕs Miniatures** candy is having the most sugar content with lowest price. Also **Nestle Smarties** candy is the most expensive with highest sugar content. 


#### Line Chart of Candy Production

we are using the candy production dataset to display a specific date and to compare production during a month to 2012

```{r Linechart}
ggplot(data = candy_production, aes(x=observation_date, y= IPG3113N)) +
  geom_line() +
  geom_smooth() +
  labs(title = "Monthly Candy Production",
 x = "Year", 
 y = "As percent of 2012 production"
 )
```


#### Bar Chart of Ingredients


```{r Barchart}
ggplot(data = candy_data, aes (x=chocolate)) +
  geom_bar()


```
```{r Barchart with Booleanfunction}
# select out the columns that have the features of the candy (chocolate, caramel, etc.)
candyFeatures <- candy_data %>% select(2:10)
# make sure that these are booleans (logical)
candyFeatures[] <- lapply(candyFeatures, as.logical)
ggplot(data = candyFeatures, aes (x=chocolate)) +
  geom_bar()
```

