---
output:
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---
# Module 3 - Assignment 3
## Pusarla, Praveenkumar
### More Practice with Plots



```{r Loading packages and data sets}
library(tidyverse)
library(readr)
GOOG <- read_csv("GOOG.csv", col_types = cols(Date = col_date(format = "%Y-%m-%d")))
head(GOOG)
```


#### Google Stock Price Plots

The following is an analysis of Google’s stock price from October of 2019 to October of 2020. This will
include a scatter, line, bar, histogram and boxplot. All the plots represent the closing price on the dates
listed on the x-axis.

```{r Diffrent kinds of Stock Price Plots}

ggplot(data = GOOG, aes (x=Date,y=Close)) +
  geom_point() +
  labs(title = "GOOG Close by Date Scatterplot",
          x = "Date", 
          y = "Close Price"
       )

ggplot(data = GOOG, aes (x=Date,y=Close)) +
  geom_line() +
  labs(title = "GOOG Close by Date Linegraph",
          x = "Date", 
          y = "Close Price"
       )

ggplot(data = GOOG, aes (x=Date,y=Close)) +
  geom_col() +
  labs(title = "GOOG Close by Date Barchart",
          x = "Date", 
          y = "Close Price"
       )


ggplot(data = GOOG, aes (Close)) +
  geom_histogram() +
  labs(title = "GOOG Close Histogram",
          x = "Close", 
          y = "Count"
       )


ggplot(data = GOOG, aes (Close)) +
  geom_boxplot() +
  labs(title = "GOOG Close Boxplot",
          x = "Close", 
          y = "Close Price Average"
       )


ggplot(data = GOOG, aes (x=Date,y=Close)) +
  geom_point(color = "blue") +
  geom_line(color = "red") +
  labs(title = "GOOG Close by Date Point and Line Graph",
          x = "Date", 
          y = "Close Price"
       )


```

The most useful plots out of all the above plots are:  

* Scatterplot - Point plot
* Linegraph 
* Point and Line graph with color

All the above graph clearly articulate the closing prices trend between October of 2019 to October of 2020

#### Google Stock Daily Price Comparisons

```{r Advanced Plots}

ggplot(GOOG) +
  geom_line(aes (x=Date, y=High, color="High"))+
  geom_line(aes (x=Date, y=Low, color="Low")) +
  labs(title = "GOOG High and Low Stock Price by Date Comparison"
       )

ggplot(GOOG) +
  geom_line(aes (x=Date, y=Open, color="Open"))+
  geom_line(aes (x=Date, y=Close, color="Close")) +
  labs(title = "GOOG Open and Close Stock Price by Date Comparison"
       )

ggplot(GOOG, aes(x=Date,y=Close)) +
  geom_area(color="black", fill="blue", aplha=.2) +
  labs(title = "GOOG Close Stock Price by Date area plot"
       )

ggplot(GOOG, aes(x=Date,y=Open)) +
  geom_area(color="blue", fill="green", aplha=.1) +
  labs(title = "GOOG Open Stock Price by Date area plot"
       ) 

```

```{r Comparing Monthly Prices}

MayPrice <- subset(GOOG, Date >"2020-04-30" & Date <"2020-06-01")
head(MayPrice)

AprPrice <- subset(GOOG, Date > "2020-03-31" & Date <"2020-05-01")
head(AprPrice)

ggplot(data=MayPrice, aes(x=Date, y=Close)) +
  geom_point() +
  geom_text(aes(label=round(Close)), size = 3, vjust = -1) +
  labs(title = "GOOG May Close Stock Price by Date with point details"
       ) 

ggplot(data=AprPrice, aes(x=Date, y=Open)) +
  geom_point() +
  geom_text(aes(label=round(Open)), size = 2, vjust = -1.5) +
  labs(title = "GOOG Apr Open Stock Price by Date with point details"
       ) 

```

