---
output:
  word_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---
# Module 3 - Assignment 2
## Pusarla, Praveenkumar
### Exploratory Data Analysis
```{r loading tidyverse}
library(tidyverse)
data("diamonds")
head(diamonds)
```

#### Diamond Color and Price

```{r Scatterplot Carat VS Price}
ggplot(data = diamonds, aes (x=carat,y=price)) +
  geom_point() 

ggplot(diamonds, aes(x=carat)) + 
  geom_histogram(binwidth=0.05)
```

* From th scatterplot between carat and prices we can clearly see a *direct relationship* between them. As the Carat size increases the price of the diamonds increases.
* From the scatterplot as well as the histogram it is quiet evident that dimonds of certain carat sizes are more predominant in the diamonds dataset example: 0.25, 0.5, 0.75, 1.0, 1.25, 1.5. 2.0 etc. 

```{r Scatterplot Color VS Price}

ggplot(data = diamonds, aes (x=color,y=price)) +
  geom_point(position='jitter')

```

* The graph shows vertical scatters for each color. Color F, G, H, I diamonds are having more high price varieties than other. But nothing much can be drawn from the scatterplot even with jitter.  

```{r Scatterplot Carat VS Price with Color}

ggplot(data = diamonds, aes (x=carat,y=price, color = color)) +
  geom_point() +
  geom_smooth()

```

* Color and Price are related. Certain color diamonds (D, E) are pricier than others (I, J). 
* Color is associated with Carat Size. Only I, J Color diamonds are available after 3.5 and above carat size.  


```{r Scatterplot Carat VS Price with Color for sample data}
head("diamonds")
dsample <- diamonds[sample(nrow(diamonds), 100),]

ggplot(data = dsample, aes (x=carat,y=price, color = color)) +
  geom_point() +
  geom_smooth(method = lm)

```


* The same plot using sample data affirms the above conclusion

```{r}

ggplot(data = diamonds, aes (x=carat,y=price, color = color)) +
  geom_boxplot()


ggplot(data = dsample, aes (x=carat,y=price, color = color)) +
  geom_line()

```

* The above boxplot and line plots clearly shows that average prices of diamonds depends on Carat size and Certain Colors of diamonds are more predominantly available with lower carat sizes. 
* Color and Carat are also related and only certain clour diamonds are available with higher carats. 



