---
output:
  word_document: default
  html_document: default
editor_options: 
  chunk_output_type: inline
---
# Module 4 - Assignment 1
## Pusarla, Praveenkumar
### Data Transformation

```{r Loadpackages and dataFiles}
library(tidyverse)
library(readr)
state_income <- read_csv("state_income.csv")
head(state_income)

```

#### State Incomes


A subset of data from the state income data file will be used for this assignment. The variables used for this exercise will be:

1. State_Name - Variable Type: *Character*
2. State_ab - Variable Type: *Character*
3. County - Variable Type: *Character*
4. City - Variable Type: *Character*
5. Type - Variable Type: *Character*
6. ALand - Variable Type: *double*
7. Mean - Variable Type: *double*
8. Median - Variable Type: *double*
9. Stdev - Variable Type: *double*

```{r Selecting and arranging}

state_income1 <- select(state_income,State_Name,State_ab,County,City,Type,ALand,Mean,Median,Stdev,everything())
head(state_income1)

state_income2 <- select(state_income,State_ab,State_Name,County,City,Type,ALand,Mean,Median,Stdev)
head(state_income2)

state_income2 <- rename(state_income2, SquareArea = ALand)
state_income2 <- rename(state_income2, IncomeMean = Mean)
state_income2 <- rename(state_income2, IncomeMedian = Median)
state_income2 <- rename(state_income2, IncomeStDev = Stdev)
head(state_income2)

NC_income <- filter(state_income2,State_ab =="NC")
head(NC_income)

```

#### NC Incomes

I will be working with NC_Income data set for this assignment to create summaries of the incomes within North Carolina 
including summaries by county, city and type. This data set contains total of 915 observation with 9 variable values.

```{r Summarization on NC income}

NC_income <- arrange(NC_income,County)

summary1 <- group_by(NC_income,County) 
summary1 <- summarise (summary1, mean= mean(IncomeMean))
head(summary1)
summary2 <- NC_income %>%
 group_by(City) %>%
 summarise (mean = mean(IncomeMean))
head(summary2)
```

The **summary1** data set contains the mean income of the NC residents by county. 
The **summary2** data set conatins the mean income of the NC residents by city.

```{r Summarization by type}

summary3 <- NC_income %>%
 group_by(Type) %>%
 summarise (mean = mean(IncomeMean))
head(summary3)

```

The **summary3** data set contains the mean income of NC residents by type.


#### Income Visualization

```{r visualization of NC data}

ggplot(data = summary1, aes (x=County,y=mean)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90,vjust =0.5, hjust=1)) +
  labs(title = "Scatterplot of NC Residents income by County",
          x = "NC County", 
          y = "Income"
       )

```

In the NC state **Wake County** has the highest average income and **Stanly County** has the lowest average income. The county with second lowest average income is **Surry County**

```{r Visuvalization for complete data}
head(state_income2)
AvgStateIncome <- state_income2 %>%
 group_by(State_ab) %>%
 summarise (mean = mean(IncomeMean))
head(AvgStateIncome)

AvgStateIncome <- filter(AvgStateIncome, grepl("N",State_ab))
head(AvgStateIncome)

ggplot(data = AvgStateIncome, aes (x=State_ab,y=mean)) +
  geom_point() +
  labs(title = "Scatterplot of US States (conatining letter N) Residents income ",
          x = "US States with Letter N", 
          y = "Income"
       )


```
The US state in the data set **"AvgStateIncome"** with highest average income is **"NJ"** and lower average income is **"TN"**
