---
output:
  word_document: default
  html_document: default
---

# Module 5 - Assignment 1
## Pusarla, Praveenkumar
### Data Wrangling
```{r library calss and file imports}
library(tidyverse)
library(readxl)
UN_migrant <- read_excel("UN_migrant.xlsx", 
    sheet = "Table 6", col_types = c("numeric", 
        "text", "text", "numeric", "text", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "text", "text", "text", "text", "numeric", 
        "numeric", "text", "text", "text", 
        "text", "text"), skip = 15)
UN_migrant
```

####  Cleaning Data with dplyr

```{r Rnaming Colums selecting specific columns}

UN_migrant <- UN_migrant %>%
  rename("Country" = "...2") %>%
  rename("Country_Code" ="...4") %>%
  rename("Type" = "...5") %>%
  rename("1990" = "1990...6") %>%
  rename("1995" = "1995...7") %>%
  rename("2000" = "2000...8") %>%
  rename("2005" = "2005...9") %>%
  rename("2010" = "2010...10") %>%
  rename("2015" = "2015...11")

Migration <- select(UN_migrant,Country,Country_Code,Type,"1990","1995","2000","2005","2010","2015")
head(Migration)


```

#### Creating tidy data using tidyr


```{r Creation of Tidy data}

Migration2 <- Migration %>% 
  pivot_longer(c('1990','1995','2000','2005','2010','2015'), names_to = 'year', values_to = 'cases')

Migration2

Migration2$year <- as.integer(Migration2$year)

```


#### Research Questions

```{r research datasets}

RegionalMigration <- Migration2 %>%
  select(Country,everything()) %>%
  filter(Country %in% c("Africa","Asia", "Europe", "Oceania", "Northern America", "South America"))

RegionalMigration

Americas <- Migration2 %>%
  select(Country,everything()) %>%
  filter(Country %in% c("Central America", "South America", "Northern America"))

Americas

```


#### Worldwide Migration based on Regions

```{r  Worldwide Migration analysis}

ggplot(RegionalMigration, mapping = aes(year, cases, color=Country)) +
  geom_point() + 
  labs(title = "Worldwide Migration",
          x = "Year", 
          y = "Migrants"
       )

ggplot(RegionalMigration, mapping = aes(year, cases, fill=Country)) +
  geom_col() +
  scale_fill_discrete(name="Region of World") + 
  labs(title = "Worldwide Migration",
          x = "Year", 
          y = "Migrants"
       ) 
  

```

**Worldwide Migration based on Regions Responses**

a. Which region in the world had the highest number of migrants in the year 2005?

Asia region has the highest number of migrants in the year 2005

b. Over the years, which region consistently has the most migrants every 5 year span? Which has the
second most?

Asia region has the most number of migrants consistently every 5 years followed by Africa 

c. What region has seen the fewest migrants over the years?

Oceania region has the fewest number of migrants over years 

d. Which plot was most useful in answering these questions and why?

I see both plots are useful. But visually bar chart provides clear indication based on the colored area on the bars representing each region

####  Americas Migration by Region

```{r Americas Migrant Analysis}

ggplot(Americas, mapping = aes(year, cases, color=Country)) +
  geom_point() + 
  labs(title = "Americas Migration",
          x = "Year", 
          y = "Migrants"
       )

ggplot(Americas, mapping = aes(year, cases, fill=Country)) +
  geom_col() +
  scale_fill_discrete(name="Americas Region") + 
  labs(title = "Americas Migration",
          x = "Year", 
          y = "Migrants"
       ) 
  


```

**Americas Migration by Region responses** 

a. In 1990, which region had the largest number of migrants for the Americas?

Central America has the highiest number of Migrants in Amreicas Regions.

b. Has this region continued to grow since 1990?

No migrents from central america drastically reduce from 1990 to 2005

c. What trends do you notice happening in the Americas over the years?

Migrants from north America  and central america are reducing where as south american migrates are incresing 

d. Specifically, has Northern America increased or decreased over the years?

Between 1990 to 1995 the NA migrants increased but from 1995 to 2015 it is decreasing 

e. Which plot was most useful in answering these questions and why?

Scatter plot was very useful in answering the above questions as it clearly show the trends.  
