---
output:
  word_document: default
  html_document: default
---

# Module 6 - Assignment 2
## Pusarla, Praveenkumar
### Statistical Analyses

```{r Loading Packages}

library(tidyverse)
library(corrplot)
library(RColorBrewer)
library(readr)
library(readxl)
Perceptions <- read_excel("Perceptions.xlsx")
Advertising <- read_csv("Advertising.csv")
Insurance <- read_csv("Insurance.csv")
RespiratoryExchangeSample <- read_excel("RespiratoryExchangeSample.xlsx")


```

#### Regression and Correlation 

Regression analysis is a statistical method that allows you to examine the relationship between two or more
variables of interest. Correlation analysis is a method of statistical evaluation used to study the strength of a
relationship between two, numerically measured, continuous variables (e.g. height and weight). This
particular type of analysis is useful when a researcher wants to establish if there are possible connections
between variables.

#### Insurance Costs

We would like to determine if we can accurately predict insurance costs based upon the factors included in
the data. We would also like to know if there are any connections between variables (for example, is age
connected or correlated to charges).

#### Correlations of bmi, age, children and cost


```{r}

Insurance2 <- select(Insurance, age, bmi, children, charges)

Corr_matrix <- cor(Insurance2)


corrplot(Corr_matrix, type="upper", order="hclust",
 col=brewer.pal(n=8, name="RdYlBu"))

```


Based on the above chart, **Variables age and Charges are highly correlated** among all the variables in the Insurance data.


#### Regression Analysis


```{r}

mlreg <- lm(charges ~ bmi + age + children, data=Insurance2)    
summary(mlreg)


```

Based on the analysis we can clearly see that the **age and bmi variables are significant impact on charges.** Age is the most significant variable on the charges. 


```{r Add new Variables}

Insurance3 <- mutate(Insurance, gender=ifelse(sex=="female",1,0))
Insurance3 <- mutate(Insurance3, smoker2=ifelse (smoker=="yes",1,0 ))

mlreg2 <- lm(charges ~ bmi + age + children + gender + smoker2, data=Insurance3)  
summary(mlreg2)


```

After adding the gender and Smoker variables, it is clear that the **smoker variables has significant impact on the charges.** 


#### Group Comparisons with t-tests

The t-test is used to compare the values of the means from two samples and test whether it is likely that the
samples are from populations having different mean values. This is often used to compare 2 groups to see if
there are any significant differences between these groups.

#### Caffeine Impacts on Respiratory Exchange Ratio

A study of the effect of caffeine on muscle metabolism used volunteers who each underwent arm exercise
tests. Half the participants were randomly selected to take a capsule containing pure caffeine one hour
before the test. The other participants received a placebo capsule. During each exercise the subject's
respiratory exchange ratio (RER) was measured. (RER is the ratio of CO2 produced to O2 consumed and is an
indicator of whether energy is being obtained from carbohydrates or fats).

The question you are trying to answer is whether caffeine impacts RER during exercise.


```{r t-test}

RespiratoryExchangeSample

summary(RespiratoryExchangeSample)

Resdf <- RespiratoryExchangeSample %>%
        filter(Placebo == 84 | Placebo == 99) %>%
        select(Placebo, Caffeine)


t.test(Caffeine ~ Placebo , Resdf)


```


As the **p values is 0.3 which concludes that there is no significant difference between the two groups.**


#### Impact of Advertising

You are a marketing researcher conducting a study to understand the impact of a new marketing campaign.
To test the new advertisements, you conduct a study to understand how consumers will respond based on
see the new ad compared to the previous campaign. One group will see the new ad and one group will see
the older ads. They will then rate the ad on a scale of 0 to 100 as a percentage of purchase likelihood based
on the ad.

The question you are trying to answer is whether to roll out the new campaign or stick with the current
campaign


```{r}

Advertising

summary(Advertising)

Advdf <- Advertising %>%
        filter(Group == 1 | Group == 2) %>%
        select(Group, Rating)

Advdf <- Advdf[complete.cases(Advdf),]

t.test( Rating ~ Group , Advdf, var.equal=TRUE)


```

As the **p values is 0.2113 which concludes that there is no significant difference between the two groups.**



#### ANOVA


An ANOVA test is a way to find out if survey or experiment results are significant. In other words, they help
you to figure out if you need to reject the null hypothesis or accept the alternate hypothesis. Basically, you’re
testing groups to see if there’s a difference between them. Examples of when you might want to test
different groups:

* A group of psychiatric patients are trying three different therapies: counseling, medication and biofeedback. You want to see if one therapy is better than the others

* A manufacturer has two different processes to make light bulbs. They want to know if one process is better than the other.

* Students from different colleges take the same exam. You want to see if one college outperforms the other.
 

#### Perceptions of Social Media Profiles


This study examines how certain information presented on a social media site might influence perceptions of trust, connectedness and knowledge of the profile owner. Specifically, participants were shown weak, average and strong arguments that would influence their perceptions of the above variables. Using the dataset provided, the following code runs an ANOVA with post-hoc analyses to understand argument strength impacts on perceptions.


 
```{r ANOVA}

Anova1 <- aov(Trust ~ Argument, data = Perceptions)

summary(Anova1)

Anova2 <- aov(Connectedness ~ Argument, data = Perceptions)

summary (Anova2)

Anova3 <- aov(Knowledge ~ Argument, data = Perceptions)

summary(Anova3)

TukeyHSD(Anova1)

TukeyHSD(Anova2)

```

**Connectedness and Trust **are significantly depend on the Argument.  

Arguments **Weak-average and Weak-Strong ** are significant for Trust. 

Arguments **Weak-average and Weak-Strong ** are significant for Connectedness
