---
output:
  word_document: default
  html_document: default
---

# Module 6 - Assignment 1
## Pusarla, Praveenkumar
### Lubridate

```{r Pacakage calls and Data Upload}
library(tidyverse)
library(lubridate)
library(readr)
Appointments <- read_csv("Appointments.csv")
Appointments
```

#### Working with Dates

```{r}
Appointments <- Appointments %>% 
    mutate(
    ReservationYear = 2019)

Appointments    

```

```{r Additing New Variables of data}

Appointments <- Appointments %>% 
    mutate(
    ReservationDate =make_date (month=ReservationMonth, day=ReservationDay, year=ReservationYear),
    CreationDate = make_date (month=CreationMonth, day=CreationDay, year=CreationYear))

Appointments

```
```{r ReservationSpan}

Appointments <- Appointments %>% 
    mutate(
    ReservationSpan = ReservationDate - CreationDate)

Appointments


```


####  Exploratory Analysis


```{r Summary}

summary(Appointments)

Appointments$ReservationSpan <- as.integer(Appointments$ReservationSpan)

summary(Appointments)

```

**Answering the question 19 of Module 6 Assignment1**

a. What is the average time between appointment creation and the actual reservation date?

The mean of ReservationSpan = 38.53 days

b. What was the max time?

The Max ReservationSpan = 207.00 days

c. What was the min time?

The Min ReservationSpan = 1.00 days



```{r Correlation}

cor(Appointments$ReservationSpan, Appointments$Show)



```


**Answering the question 20 of Module 6 Assignment1**

a. Are ReservationSpan and Show highly correlated?

As per the correlation output between ReservationSpan and Show present on the Appointments data it can be concluded that they are not much related


```{r barchart}

ggplot(data = Appointments, aes (x=Show)) +
  geom_bar(width = 0.1) +
  labs(title = "Bar chart of Show ",
          x = "Show", 
          y = "Count"
       )


```

**Answering the question 21 of Module 6 Assignment1**


a. Based on 0 being “no show” and 1 being “show”, did most people make their appointments?

Based on the bar char we can say that most the people are showing up to the appointments



