# Assignemen1 Module2

```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest) #for the Durbin-Watson test
```

```{r data set}

air = airquality

str(air)
summary(air)

```

1. Number of rows **153**
2. Number of columns **6**
3. There is a missing data in Ozone variable - **True**

```{r}
ggpairs(air)
```
```{r}
ggplot(air,aes(x=Ozone,y=Temp)) + geom_point(alpha=0.5) + theme_bw()
```

4. Which variable is most likely be a response of variable - **Temp** or **OZone**

```{r}

air2 = air %>% drop_na()
str(air2)
summary(air2)
```

5. rows in air2 **111**
6. columns in air2 **6**

```{r}

ggpairs(air2)

ggcorr(air2, lable = "TRUE")

```


7. Variabl emost strongly related  with Ozone is **Temp**

8. Which of the variable is least strongly related with Ozone is **Day**

```{r}
ggplot(air,aes(x=Temp,y=Ozone)) + geom_point(alpha=0.5) + theme_bw()
```

Q9. **As temp Increase Ozone increase**


```{r}
#reusing code from before (just changing names where needed)
air_simple = recipe(Ozone ~ Temp, air2)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(air_simple)

lm_fit = fit(lm_wflow, air2)
```

```{r}
summary(lm_fit$fit$fit$fit)
```

10. Slope = **2.4391**
11. R-squared = **0.488**
12. Temp variable is significant in the model -  **Yes**
13. 
```{r}
temp_var = predict(lm_fit$fit$fit$fit, interval = "prediction") #accessing the fit object with the three $fit
new_df = cbind(air2, temp_var)

ggplot(new_df, aes(x = Temp, y = Ozone)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  geom_line(aes(y=lwr), color = "red", linetype = "dashed") +
  geom_line(aes(y=upr), color = "red", linetype = "dashed") +
  theme_bw() 

confint(lm_fit$fit$fit$fit)
```

Q13 **False**




```{r}
#Manually
-147.6461 + 2.4391*80

#Using predict function
testdata = data.frame(Temp = 80)
predict(lm_fit, new_data = testdata)

```



```{r}
dwtest(lm_fit$fit$fit$fit)
```

We fail to reject the null hypothesis with a p-value greater than 0.05. This suggests that the residuals are likely independent.


