---
output:
  word_document: default
  html_document: default
---
### R Studio Refresher assignment

```{r}
library(tidyverse)

diamonds = ggplot2::diamonds # Q1 code
str(diamonds)

```

Question 1: The “ggplot2” package (part of the tidyverse set of packages) includes a dataset containing
data on diamonds. Use the line of code below to read in this dataset into a data frame called “diamonddata”.
Use an appropriate R command to answer the question: 
How many rows are in this dataset? **53940**

Question 2: How many columns are in the “diamonds” dataset? **10**

Question 3: Using ggplot, create a scatterplot of caret (x axis) versus price (y axis). Which statement best
describes the relationship between “caret” and “price”?



```{r}
ggplot(diamonds, aes(x=carat,y=price)) +geom_point() + theme_bw()
```

Q3 Answer is **B. As caret increases price increases**

Question 4: Repeat Question 3, but in this plot color the scatterplot points by the “cut” variable. Which
statement best describes the relationship between “cut” and “price”?
A. As cut quality increases price increases
B. As cut quality decreases price increases
C. As cut quality increases price does not change

```{r}

ggplot(diamonds, aes(x=carat,y=price, color=cut)) +geom_point() + theme_bw()

```
Q4 : Answer **A. As cut quality increases price increases**



Question 5: Repeat Question 4, but in this plot you should facet by “color”. Faceting a plot is described at
this link: http://www.cookbook-r.com/Graphs/Facets_(ggplot2)/.
What does “faceting” do to the plot?
A. Creates a separate scatterplot for each “cut”
B. Creates a separate scatterplot for each “carat”
C. Creates a separate scatterplot for each “color”
D. Creates a separate scatterplot for each “price”


```{r}

ggplot(diamonds, aes(x=carat,y=price, color=cut)) +geom_point() + theme_bw() + facet_grid(color ~ .)

```
Q5 Answer: **C. Creates a separate scatterplot for each “color”**



Question 6: Use the “read_csv” function to read-in the “InventoryData.csv” file as a data frame called
“inventory”. NOTE: In this course we will ALWAYS (unless instructed otherwise) use the “read_csv” command.
Do NOT use the “read.csv” command.
In the “inventory” data frame that you have just created, what type of variable is “Supplier”?
A. numeric
B. integer
C. factor
D. character

```{r}
library(readr)
InventoryData <- read_csv("InventoryData.csv")
InventoryData
str(InventoryData)
```
Q6 Answer **D. character**

Question 7 In the “inventory” data frame that you have just created, what is the mean of the “On Hand”
variable?

```{r}
invmean = InventoryData %>% summarise(invmean = mean(`On Hand`))

invmean


```


Q7 Answer **quantity of Items present in the store belomning to a specific supplier's item number** 


Question 8: Use a filter to create a new data frame called “inventoryA” containing only inventory from
Supplier A. How many rows are in this new data frame?


```{r}

inventoryA = InventoryData %>% filter (Supplier == "A")
str(inventoryA)
```

Q8 Answer **3695 rows**

Question 9: What does the line of code shown below do? Note the use of the backtick character (on the
tilde key on your computer’s keyboard) to delineate the variable names with spaces in them.
inventoryA = mutate(inventoryA, OnHandRatio = `On Hand`/ `Annual Demand`)
A. Creates a new variable called “inventoryA”
B. Creates a new variable called “OnHandRatio”
C. Creates a new data frame called “OnHandRatio”

```{r}
inventoryA = mutate(inventoryA, OnHandRatio = `On Hand`/`Annual Demand`)
#inventoryA = mutate(inventoryA, OnHandRatio = on Hand/Annual Demand)
str(inventoryA)
```
Q9 Answer **B. Creates a new variable called “OnHandRatio”**

Question 10: Using the “inventoryA” object that you created in Question 9, create a new data frame called
“avg_cost” that contains the average “Cost per Unit ($)” by each “Item SKU” (let this quantity be in a
variable called “SKUAvgCost. Hint: Recall the summarize and group_by functions and the use of the backtick
character from Task 8. Your data frame should have only two columns:”Item SKU” and “SKUAvgCost”.
What is the “SKUAvgCost” of items with an “Item SKU” of 011?


```{r}

avg_cost = inventoryA %>% group_by(`Item SKU`) %>% summarise(SKUAvgCost = mean(`Cost per Unit ($)`))
avg_cost #display the newly grouped and summarized data

```

Q10 Answer **12.330000**

